---
name: Junliang "Julian" Tao
address: "School of Sustainable Engineering and the \\tabularnewline Built Environment,\\tabularnewline Arizona State University, AZ, 85286"
www: juliantao.github.io/big/
email: "julian.tao@asu.edu"
scholar: "U5L3d1cAAAAJ"
orcid: "0000-0002-3772-3099"
github: juliantao
date: today 
date-format: "MMMM YYYY"
position: PhD, Associate Professor
fontsize: "12pt"
format: cv-pdf
header-includes:
  - \geometry{left=1in,right=1in,top=1in,bottom=1in}
---

\titlespacing{\section}{0pt}{1.ex}{0.5ex}
\thispagestyle{empty}

```{r import} 
source("preprocess.R")
```


# Education 

```{r degrees, results='asis'}
tribble(
  ~Degree, ~Area, ~Insitution, ~State, ~Years,
  "\\textbf{PhD} ", "Civil Engineering", "Case Western Reserve University", "Cleveland, US", "2013",
  "\\textbf{MS} ", "Civil Engineering", "Tongji University", "Shanghai, China", "2009",
  "\\textbf{BS} ", "Civil Engineering", "China University of Geosciences", "Wuhan, China", "2006"
) %>%
  baretable()
```

# Experiences

```{r employment, results='asis'}
tribble(
  ~Start, ~End, ~Position,
  2018, NA, "\\textbf{Associate Professor}, School of Sustainable Engineering and the Built Environment, Arizona State University",
	2022, 2022, "\\textbf{Guest Professor}, Institute of Geotechnical Engineering, University of Natural Resources and Life Sciences (BOKU)",
  2013, 2018, "\\textbf{Assistant Professor}, Department of Civil Engineering, University of Akron"
) |>
  arrange(-Start) |>
  mutate(
    Start = as.character(Start),
    End = as.character(End),
    End = tidyr::replace_na(End, ""),
    Years = if_else(End == Start,
      as.character(Start),
      paste(Start, "--", End, sep = ""),
      paste(Start, "--", End, sep = "")
    )
  ) |>
  select(Years, Position) |>
  baretable(
            align = "lp{1in}p{5.5in}"
  )
```

# Selected awards and honours

```{r awards, results='asis'}
awards <- tribble(
  ~Year, ~Award,
  2017, "CAREER Award, National Science Foundation",
  2017, "Young Engineer of the Year Award, American Society of Civil Engineers, Akron Section"
) %>%
  baretable()
```

# Professional Membership and Service

```{r member, results='asis'}
member <- tribble(
  ~Type, ~Org,
  "Associate Member", "American Society of Civil Engineers (ASCE) Geo-Institute",
  "Member", "Institute of Electrical and Electronics Engineers (IEEE)",
  "Member", "International Society for Soil Mechanics and Geotechnical Engineering (ISSMGE)",
  "Member", "Society for Integrative and Comparative Biology (SICB)",
) %>%
  baretable(
            align = "lp{1.5in}p{5in}"
  )
```

\vspace{0.5ex}

I have participated in organizing or chairing `r nconf_participated` technical conferences or sessions, served on `r ncommittee_profession` technical committees, and reviewed for `r nreview_journal` journals, `r nreview_agency` funding agencies. I also volunteered in `r noutreach` outreach activities.

# Relevant Publications 

Since 2009 I have authored `r npub` research publications, including `r narticle` journal papers, `r nproceeding` conference papers, and `r nreport` technical reports, co-edited `r nbook` books, and filed `r npatent` patents.
I also have delivered `r ntalk` invited talks to universities, local, national and international conferences.
As of `r format(Sys.time(), "%B %e, %Y")`, my h-index is `r jtcite$All[2]` and i10-index is `r jtcite$All[3]`, with total citations of `r prettyNum(jtcite$All[1], big.mark=",")`. (**Bold**: PhD student, ^#^: undergrad student, ^\*^: corresponding)

```{r selectpub}
#| output: asis
jtpubs[c(
         "HTB+20", "Tao21", "THT20a", "THT19", "TT22", "ZHT23", "SPT23", "ZT23", "ZT22a", "STLT23"
  )] |>
  add_bib_section()
```


# Relevant Qualifications, Capabilities, and Experiences


I am the director of the research group Bio-inspired Geotechnics (BiG) in the NSF Research Center for Bio-mediated and Bio-inspired Geotechnics at Arizona State University.
We seek the answers at the boundaries of biology, mechanics and engineering. We achieve the BiG goals and extend the impacts from research, teaching, outreach, entrepreneurship and collaboration.
Our Current research topics include: bio-inspired self-burrowing robots, bio-inspired underground sensing and communication, bio-inspired sustainable countermeasures to natural hazards.

\vspace{1em}

I have secured about \$2M awards as a PI, published over 100 research papers, mentored about 20 graduate students, about 30 undergraduate and high school students, and a number of high-school teachers. Among all my mentees, about 1/3 are from underrepresented groups.

\vspace{1em}

My leadership is demonstrated through organizing the upcoming International Conference on Bio-mediated and Bio-inspired Geotechnics, and co-editing several proceedings and special journal issues in bio-inspired geotechnics.


