---
name: Junliang "Julian" Tao
address: "School of Sustainable Engineering and the Built Environment,\\tabularnewline Arizona State University, AZ, 85286"
www: juliantao.github.io/big/
email: "julian.tao@asu.edu"
scholar: "Dq4lhi4AAAAJ"
orcid: "0000-0002-3772-3099"
github: juliantao
date: "`r format(Sys.Date(), '%B %Y')`"
date-format: "MMMM YYYY"
position: PhD, Associate Professor
fontsize: "11pt"
format: cv-pdf
header-includes:
  - \geometry{left=1.5cm,right=1.5cm,top=2cm,bottom=1cm}
---

\titlespacing{\section}{0pt}{1.ex}{0.5ex}
\thispagestyle{empty}

```{r import} 
source("preprocess.R")
```

# Education 

```{r degrees, results='asis'}
tribble(
  ~Degree, ~Area, ~Insitution, ~State, ~Years,
  "\\textbf{PhD} ", "Civil Engineering", "Case Western Reserve University", "Cleveland, US", "2013",
  "\\textbf{MS} ", "Civil Engineering", "Tongji University", "Shanghai, China", "2009",
  "\\textbf{BS} ", "Civil Engineering", "China University of Geosciences", "Wuhan, China", "2006"
) %>%
  baretable()
```

# Experiences

```{r employment, results='asis'}
tribble(
  ~Start, ~End, ~Position,
  2018, NA, "\\textbf{Associate Professor}, School of Sustainable Engineering and the Built Environment, Arizona State University",
	2022, 2022, "\\textbf{Guest Professor}, Institute of Geotechnical Engineering, University of Natural Resources and Life Sciences (BOKU)",
  2013, 2018, "\\textbf{Assistant Professor}, Department of Civil Engineering, University of Akron"
) |>
  arrange(-Start) |>
  mutate(
    Start = as.character(Start),
    End = as.character(End),
    End = tidyr::replace_na(End, ""),
    Years = if_else(End == Start,
      as.character(Start),
      paste(Start, "--", End, sep = ""),
      paste(Start, "--", End, sep = "")
    )
  ) |>
  select(Years, Position) |>
  baretable(
            align = "lp{1in}p{5.5in}"
  )
```

# Selected awards and honours

```{r awards, results='asis'}
awards <- tribble(
  ~Year, ~Award,
  2017, "CAREER Award, National Science Foundation",
  2017, "Young Engineer of the Year Award, American Society of Civil Engineers, Akron Section"
) %>%
  baretable()
```

# Professional Membership and Service

```{r member, results='asis'}
member <- tribble(
  ~Type, ~Org,
  "Associate Member", "American Society of Civil Engineers (ASCE) Geo-Institute",
  "Member", "Institute of Electrical and Electronics Engineers (IEEE)",
  "Member", "International Society for Soil Mechanics and Geotechnical Engineering (ISSMGE)",
  "Member", "Society for Integrative and Comparative Biology (SICB)",
) %>%
  baretable(
            align = "lp{1.5in}p{5in}"
  )
```

\vspace{0.5ex}

I have participated in organizing or chairing `r nconf_participated` technical conferences or sessions, served on `r ncommittee_profession` technical committees, and reviewed for `r nreview_journal` journals, `r nreview_agency` funding agencies. I also volunteered in `r noutreach` outreach activities.

# Patents, Publications, and Invited Talks

Since 2009 I have authored `r npub` research publications, including `r narticle` journal papers, `r nproceeding` conference papers, and `r nreport` technical reports, co-edited `r nbook` books, and filed `r npatent` patents.
I also have delivered `r ntalk` invited talks to universities, local, national and international conferences.
As of `r format(Sys.time(), "%B %e, %Y")`, my h-index is `r jtcite$All[2]` and i10-index is `r jtcite$All[3]`, with total citations of `r prettyNum(jtcite$All[1], big.mark=",")`.

```{r selectpub}
#| output: asis
jtpubs[c(
         "HTB+20", "Tao21", "THT20a", "THT19", "TT22", "TY12", "ZHT23", "ZT22a"
  )] |>
  add_bib_section()
```
